---
title: "Doñana_frugyvory_camptrap"
author: "PVA"
date: "6/7/2023"
output: html_document
---
The following script is an example of the workflow needed to compile the information from camera traps for ecological interactions in the data-paper Frugivory-camtrap. Note that this example only uses data from the species Arbutus unedo during the second fruiting season monitored (2022-2023). The input file is a .csv that have been visualized and tagged in the TimeLapse visualization program (Greenberg ####) after a Megadetector (AI) run to remove blank videos.   

Libraries
```{r}
library(dplyr)
library(stringr)
library(lubridate)
```
# 1. SAMPLING EFFORT 
## 1. Read the data with sampling efforts from camera trap survey
```{r }
sampling_effort <- read.csv("/Users/Pablo/Documents/GitHub/donana-frugivory-camtrap/Metadata/Sampling_effort/raw_effort/video_yr2.csv", sep=";") %>%
  filter(grepl("Aune", deployment)) %>%
  mutate(Plant_ID = str_sub(deployment, start = 1L, end = 7)) #Maybe introduce this column in the sampling effort.csv before reading.
```

## 2. GROUP effort for plant species level and for individual plant level 
```{r }
#Species level
eff_sp_level <- sum(sampling_effort$num_days)

#Individual level  
eff_ind_level <- sampling_effort %>%
   group_by(Plant_ID) %>%
   summarise(effort_ind = sum(num_days))

#Revision level
eff_rev <- data.frame(sampling_effort %>%
  group_by (Plant_ID, rev) %>%
  summarise(effort_rev = sum(num_days),
            n_cam = n(), 
            ID = str_c(Plant_ID, rev, sep="_" ))) %>%
  select(ID, n_cam, effort_rev)

```


# DATA MERGING
## 0. Prepare toy dataset
```{r }
#Prepare Aune data
Aune_data <-  read.csv2 ("/Users/Pablo/Documents/GitHub/Animal-detection-cameratrap/Results/Timelapse results Yr2/Arbutus_yr2_revised_c01.csv", sep = ",") 
  
splited_path <- data.frame(str_split_fixed(Aune_data$RelativePath, "\\\\", 4))%>%
  rename(Folder = X1, Plant = X2, Revision = X3, Deployment = X4) %>%
  mutate(Revision = str_remove_all(Revision, "Aune_"),
         Revision = str_sub(Revision, start = 1, end = 5))

Revision <- data.frame(splited_path$Revision) %>%
  rename(Revision = splited_path.Revision)

Deployment_ID <- data.frame(splited_path$Deployment)%>%
  rename(Deployment_ID = splited_path.Deployment)

Plant_ID <- data.frame(str_sub(splited_path$Deployment, start=1, end = 7)) %>%
  rename(Plant_ID = str_sub.splited_path.Deployment..start...1..end...7.)

Aune_data2 <- Aune_data %>%
  mutate(Path = str_c(RelativePath, File, sep = "/"),
         Path = str_replace_all(Path, "\\\\", "/"),
         Path = str_remove_all(Path, "SUMHAL_YR2/Arbutus/Aune_"))%>%
  cbind(Revision, Deployment_ID, Plant_ID)

#change counts
Aune_data2$Count1 <- ifelse(Aune_data2$Sp1 != "", 1, Aune_data2$Count1)
Aune_data2$Count2 <- ifelse(Aune_data2$Sp2 != "", 1, Aune_data2$Count2)

#Select columns
Aune_data3 <- Aune_data2 %>%
  select(File, Path, Plant_ID, Revision, DateTime, Behaviour, Sp1, Count1, Sp2, Count2, Behaviour2, Deployment_ID)

write.csv(Aune_data3, "/Users/Pablo/Documents/GitHub/donana-frugivory-camtrap/Metadata/raw_data/toy_dataset.csv")

#Thing to do before reading:
  #Change counts from raw data count == 0 should be 1. 
  #Include revision Revision = str_sub(Path, start = 1, end = 5)

#----------------------------------------------------------

#Prepare file info 
file_info <- read.csv2 ("/Users/Pablo/Documents/GitHub/donana-frugivory-camtrap/Metadata/File_info_HD/file_info.csv", sep=",") %>%
  filter(grepl("Aune", Path)) %>%
  select(Path, duration) %>%
  mutate(Path = str_remove_all(Path, "/Volumes/G-RAID/SUMHAL/Arbutus/"),
         Path = str_remove_all(Path, "/Volumes/G-RAID-3/SUMHAL_YR2/Arbutus/Aune_"))

write.csv(file_info, "/Users/Pablo/Documents/GitHub/donana-frugivory-camtrap/Metadata/File_info_HD/toy_file_info.csv")

colnames(Aune_data2)
```

## 1. Load video level data - The data is the output after the visualization with TimeLapse.
```{r }
Aune_data <- read.csv("/Users/Pablo/Documents/GitHub/donana-frugivory-camtrap/Metadata/raw_data/toy_dataset.csv")
```

## 2. Include video duration 
```{r }
#Summary list of file metadata extracted from Hard drive files
file_info <- read.csv2 ("/Users/Pablo/Documents/GitHub/donana-frugivory-camtrap/Metadata/File_info_HD/toy_file_info.csv", sep=",")

#join data and file list
Aune_dat <- Aune_data %>%
  left_join(file_info, by = "Path")
```

## 3. Include sampling effort 
```{r }
Aune_dat_effort <- Aune_dat %>%
  mutate(ID = str_c(Plant_ID, Revision, sep = "_"),
         effort_sp_level = eff_sp_level) %>%
  left_join(eff_ind_level, by = "Plant_ID") %>%
  left_join(eff_rev, by = "ID") %>%
  distinct()
```

## 4. Include coordinates 
```{r }
coord <- read.csv("/Users/Pablo/Documents/GitHub/donana-frugivory-camtrap/Metadata/Coordinates/coordinates_13_spp.csv") %>%
  filter(grepl("aune", Plant_ID)) %>%
  mutate(Plant_ID = str_to_sentence(Plant_ID))
  
Aune_dat_coord <- Aune_dat_effort %>%
  left_join(coord, by = "Plant_ID")
```

## 5. Filter eating behaviours - 2,662 rows 
```{r }
Aune_eating <- Aune_dat_coord %>%
  filter(Behaviour == "eating"| Behaviour == "probably eating" | Behaviour == "searching for food")
```

## 6. Split entries with two species.
We will duplicate the entries where there are two species (SP2 = "non empty") and rename Sp1 with Sp2 name. The rest of the columns will maintain invariable (traceable through Plant_ID/Rev/File). A new column "Coexistence" will be created for searching events with more than one species.
```{r }
# Rows with only one species  - 2,576 row
rows_wo_sp2 <- Aune_eating %>%
 filter(is.na(Sp2) | nchar(Sp2) == 0) %>%
  mutate(Coexistence = FALSE)

# Rows with two species: change Sp2 to Sp1 - 62 rows (Duplicate rows based on Sp2 and Behaviour2 conditions) 
new_rows_for_sp2 <- Aune_eating %>%
  filter(!is.na(Sp2) & nchar(Sp2) > 0 & Behaviour2 %in% c("eating", "probably eating", "searching for food")) %>%
  mutate(Sp1 = Sp2,
         Count1 = Count2,
         Behaviour = Behaviour2,
         Coexistence = TRUE)

# Combine the original data with the duplicated rows should be 2,638 rows
Aune_split <- bind_rows(rows_wo_sp2 , new_rows_for_sp2) %>%
  select(!c (Sp2, Count2, Behaviour2)) 
```

## 7. Collapse videos into 5 min events

```{r}
#check
Aune_collapsed <- Aune_split %>%
  group_by (Plant_ID, Revision) %>%
  mutate(interval = as.POSIXct(round(as.numeric(as.POSIXct(DateTime)) / (60*5)) * (60*5), origin="1970-01-01")) %>%
  group_by(interval, Sp1) %>%
  summarize(File = paste(File, collapse=', '),
            Plant_ID = first(Plant_ID),
            Revision = first(Revision),
            DateTime = first(DateTime),
            AnimalSpecies = paste(Sp1, collapse=', '),
            Behaviour = paste(Behaviour, collapse=', '),
            Count = max(Count1),
            Coexistence = first(Coexistence),
            n_cam = first(n_cam),
            EffortRev = first(effort_rev),
            EffortSpLevel = first(effort_sp_level),
            EffortInd = first(effort_ind),
            n = n(),
            Duration = sum(duration),
            Long = first(Long),
            Lat = first(Lat)) %>%
  mutate(videos_events = sqrt(n*12),  # 5 minute interval, so 12 intervals per hour
         ID = first(ID)) #To select later on Timestamp Issue fixing


str(Aune_collapsed)
names(Aune_split)
names(sumhal_data)

```

## 8. Fix Timestamp Issues
```{r }

```
## 9. Give final format for publication
```{r }

```

## 

## 9. Give final format to database for publication
```{r }
# -------  Give a Revision number for "plen" 
#Filter only Pistacia lentiscus
pistacia <- data8 %>%
  filter(Plant == "plen") %>%
  mutate(Revision_ID = pistacia_rev) #Run the code below to create pistacia revision

#Create a revision number based on each visit to the field (based on the day from DateTime column) 
date_string <- format(pistacia$DateTime, "%Y-%m-%d")
revision_number <- match(date_string, unique(date_string))
pistacia_rev <- paste("Rev", revision_number, sep = "")

#Remove plen from data8 and join it again with the new revision column.
data9 <- data8 %>%
  filter(Plant != "plen") %>%
  bind_rows(pistacia)

# ---------  Add a 0 to all Corema Plant_IDs for consistency with the rest of species "Calb001" instead of "Calb01"
data10 <- data9 %>%
  mutate(Plant_ID = str_replace_all(Plant_ID, "calb", "calb0"),
         Revision_ID = str_to_sentence(Revision_ID))

# --------  Change Plant species acronyms for the entire scientific name and change colnames
data11 <- data10 %>%
  mutate(Plant = str_replace_all(Plant, "aspa" , "Asparagus aphyllus"),
         Plant = str_replace_all(Plant, "aune" , "Arbutus unedo"),
         Plant = str_replace_all(Plant, "calb" , "Corema album"),
         Plant = str_replace_all(Plant, "joxy" , "Juniperus oxycedrus"),
         Plant = str_replace_all(Plant, "jpho" , "Juniperus phoenicea"),
         Plant = str_replace_all(Plant, "mcom" , "Myrtus communis"),
         Plant = str_replace_all(Plant, "oeur" , "Olea europaea"),
         Plant = str_replace_all(Plant, "olan" , "Osyris lanceolata"),
         Plant = str_replace_all(Plant, "pbou" , "Pyrus bourgeana"),
         Plant = str_replace_all(Plant, "plen" , "Pistacia lentiscus"),
         Plant = str_replace_all(Plant, "rper" , "Rubia peregrina"),
         Plant = str_replace_all(Plant, "rulm" , "Rubus ulmifolius"),
         Plant = str_replace_all(Plant, "sasp" , "Smilax aspera"),
         Sp1 = str_to_sentence(Sp1),
         Sp1 = str_replace_all(Sp1, "Rattus", "Rattus rattus")) %>%
    rename(AnimalSpecies = Sp1, PlantSpecies = Plant, PlantID = Plant_ID, RevisionID = Revision_ID, NCam = n_cam, EffortRev = Days, Duration = duration, EffortSpecies = effort_pl_sp, EffortInd = effort_ind, Longitude = Long, Latitude = Lat) %>%
  select(-c(Days.in.field, ID))

# -------- Rule for Behavior (If there are more than one behaviors in a collapsed observation we choose the most frugivor related one i.e eating > prob. eating > searching for food)
#a - eating
#b - probably eating
#c - searching for food

data12 <- data11 %>%
  mutate(Behav = Behaviour,
         Behav = str_replace_all(Behav, "feeding", "eating"),
         Behav = str_replace_all(Behav, "probably eating", "b"),
         Behav = str_replace_all(Behav, "prob_eating", "b"),
         Behav = str_replace_all(Behav, "eating", "a"),
         Behav = str_replace_all(Behav, "searching for food", "c"),
         Behav = ifelse(grepl("a",Behav), "eating",Behav),
         Behav = ifelse(grepl("b",Behav), "probably eating",Behav),
         Behav = ifelse(grepl("c",Behav), "searching for food",Behav)) %>%
  select(-Behaviour) %>%
  rename(Behaviour = Behav)

# -------- Unify decimal numbers for each column
data13 <- data12 %>%
  mutate(Duration = round(as.numeric(Duration), 1),
         EffortRev = round(as.numeric(EffortRev), 2),
         EffortInd = round(as.numeric(EffortInd), 2), 
         EffortSpecies = round(as.numeric(EffortSpecies), 2))

# -------- Fix Revision number format (add a 0 if the RevisionID mathces the pattern "Rev" followed by a single digit)
data14 <- data13 %>%
  mutate(RevisionID = case_when(
    grepl("^Rev\\d$", RevisionID) ~ paste0("Rev0", substr(RevisionID, start = 4, stop = nchar(RevisionID))),
    TRUE ~ RevisionID)) 

# -------- Change names from Gr. Sylvia maintaining S.atricapilla and S.borin
data15 <- data14 %>%
  mutate(AnimalSpecies = str_replace_all(AnimalSpecies, "Sylvia", "Curruca"),
         AnimalSpecies = str_replace_all(AnimalSpecies, "Curruca atricapilla", "Sylvia atricapilla"),
         AnimalSpecies = str_replace_all(AnimalSpecies, "Curruca borin", "Sylvia borin"))

#write.csv(data15, "/Users/Pablo/Documents/GitHub/donana-frugivory-camtrap/Dataset_2023_07_19/DataS1_corrected_sylvia.csv")

```



