---
title: "Frugyvory_camptrap"
author: "PVA"
date: "14/8/2023"
output: html_document
---
The provided script illustrates the workflow employed to compile the data produced by camera traps for ecological interactions in the data paper "Frugivory-camtrap". Note that this example uses data from the plant species "Arbutus unedo" during the monitoring of the second fruiting season (2022-2023). The input file is a plain text (csv) generated after visualizing and tagging in TimeLapse visualization program (Greenberg, 2020) and after a Megadetector (Beery et al. 2019) run to remove blank videos.   


Libraries and directory.
```{r , include=FALSE}
library(here)
library(dplyr)
library(stringr)
library(lubridate)

knitr::opts_chunk$set(echo = TRUE)
folder <- here("Code/example_raw_data")
```

# 1. SAMPLING EFFORT 
## 1.1. Read the data with sampling efforts from camera trap survey
```{r }
#Sampling effort data for Arbutus unedo (second fruiting season)
sampling_effort <- read.csv(file.path(folder, "sampling_effort.csv"))
```

## 1.2. GROUP effort for plant species level and for individual plant level 
```{r }
#Species level
eff_sp_level <- sum(sampling_effort$num_days)

#Individual level  
eff_ind_level <- sampling_effort %>%
   group_by(Plant_ID) %>%
   summarise(effort_ind = sum(num_days))

#Revision level (and TimestampIssues)
eff_rev <- data.frame(sampling_effort %>%
  group_by (Plant_ID, rev) %>%
  summarise(effort_rev = sum(num_days),
            n_cam = n(), 
            ID = str_c(Plant_ID, rev, sep="_" ))) %>% 
  select(ID, n_cam, effort_rev)
```

# DATA MANAGENEMT
## 1. Load video level data                             - 10,827 rows 
The data is the output after the visualization with TimeLapse.
```{r }
Aune_data <-  read.csv(file.path(folder, "example_dataset.csv"))
```

## 2. Include video duration                            - 10,827 rows
```{r }
#Summary list of file metadata extracted from Hard drive files
file_info <- read.csv(file.path(folder, "file_info.csv"))  %>%
  select(Path, duration)

#join data and file list
Aune_dat <- Aune_data %>%
  left_join(file_info, by = "Path")
```

## 3. Include sampling effort                           - 10,827 rows 
```{r }
Aune_dat_effort <- Aune_dat %>%
  mutate(ID = str_c(Plant_ID, Revision, sep = "_"),
         effort_sp_level = eff_sp_level) %>%
  left_join(eff_ind_level, by = "Plant_ID") %>%
  left_join(eff_rev, by = "ID") %>%
  distinct()
```

## 4. Include coordinates                               - 10,827 rows
```{r }
coord <- read.csv(file.path(folder, "coordinates.csv"))

Aune_dat_coord <- Aune_dat_effort %>%
  left_join(coord, by = "Plant_ID")
```

## 5. Filter eating behaviours                          - 2,662 rows 
```{r }
Aune_eating <- Aune_dat_coord %>%
  filter(Behaviour == "eating"| Behaviour == "probably eating" | Behaviour == "searching for food")
```

## 6. Split entries with two species                    - 2,724 rows
We will duplicate the entries where there are two species (SP2 = "non empty") and rename Sp1 with Sp2 name. The rest of the columns will maintain invariable (traceable through Plant_ID/Rev/File). A new column "Coexistence" will be created for searching events with more than one species.
```{r }
# Videos containing one species alone  - 2,576 row
rows_wo_sp2 <- Aune_eating %>%
 filter(is.na(Sp2) | nchar(Sp2) == 0) %>%
  mutate(Coexistence = FALSE)

# Videos containing two different species: here we change Sp2 to Sp1 - 62 rows (Duplicate rows based on Sp2 and Behaviour2 conditions) 
new_rows_for_sp2 <- Aune_eating %>%
  filter(!is.na(Sp2) & nchar(Sp2) > 0 & Behaviour2 %in% c("eating", "probably eating", "searching for food")) %>%
  mutate(Sp1 = Sp2,
         Count1 = Count2,
         Behaviour = Behaviour2,
         Coexistence = TRUE)

new_rows_for_sp1 <- Aune_eating %>%
  filter(!is.na(Sp2) & nchar(Sp2) > 0 & Behaviour %in% c("eating", "probably eating", "searching for food")) %>%
  mutate(Coexistence = TRUE)

# Combine the original data with the duplicated rows should be 2,638 rows
Aune_split <- bind_rows(rows_wo_sp2 , new_rows_for_sp2, new_rows_for_sp1) %>%
  select(!c (Sp2, Count2, Behaviour2)) 
```

## 7. Remove unknown species and correct inconsitencies - 2,712 rows
```{r}
#Remove unknown species and correct some inconsistent names for Sp1
df1 <- Aune_split %>%
  filter( Sp1 != "?", 
          Sp1 != "") %>%
  mutate( Sp1 = str_to_sentence(Sp1))

#Rectify inconsistent names resulting from manual typing during the visualization process.  
df1$Sp1 [df1$Sp1 == "Fr" ] <- "Fringilla coelebs"
df1$Sp1 [df1$Sp1 == "Turdus me" ] <- "Turdus merula"
df1$Sp1 [df1$Sp1 == "Sylvia melanocephala" ] <- "Curruca melanocephala"
```

## 8. Collapse videos into 5 min events                 - 1,758 rows
```{r}
Aune_collapsed <- df1 %>%
  group_by(Plant_ID, Revision) %>%
  mutate(interval = as.POSIXct(round(as.numeric(as.POSIXct(DateTime)) / (60*5)) * (60*5), origin="1970-01-01")) %>%
  group_by(interval, Sp1) %>%
  summarize( 
    n = n(),
    PlantSp = "Arbutus unedo",
    Plant_ID = first(Plant_ID),
    File = paste(File, collapse=', '),
    Count = max(Count1),
    DateTime = first(as.POSIXct(DateTime)),
    Behaviour = paste(Behaviour, collapse=', '),
    Coexistence = first(Coexistence),
    N_cam = first(n_cam),
    EffortRev = first(effort_rev),
    EffortSpecies = first(effort_sp_level),
    EffortInd = first(effort_ind),
    duration = sum(as.numeric(duration)),
    long = first(Long),
    lat = first(Lat),
    Revision_ID = first(Revision),
    Deployment_ID = first(Deployment_ID),
    ID = first(ID)
                              ) %>%
  rename(AnimalSpecies = Sp1) %>%
  data.frame()
```

## 9. Give final format to database for publication     - 1,758 rows
```{r }
# -Rule for Behavior (If there are more than one behavior in a collapsed event we choose the alternative according to the following order: 1. eating > 2. prob. eating > 3. searching for food)
df2 <- Aune_collapsed %>%
  mutate(Behav = Behaviour,
         Behav = str_replace_all(Behav, "probably eating", "b"),
         Behav = str_replace_all(Behav, "eating", "a"),
         Behav = str_replace_all(Behav, "searching for food", "c"),
         Behav = ifelse(grepl("a",Behav), "eating",Behav),
         Behav = ifelse(grepl("b",Behav), "probably eating",Behav),
         Behav = ifelse(grepl("c",Behav), "searching for food",Behav)) %>%
  select(-Behaviour) %>%
  rename(Behaviour = Behav)

# Unify decimal numbers
df3 <- df2 %>%
  mutate(duration = round(as.numeric(duration), 1),
         EffortRev = round(as.numeric(EffortRev), 2),
         EffortInd = round(as.numeric(EffortInd), 2), 
         EffortSpecies = round(as.numeric(EffortSpecies), 2),
         long = round(as.numeric(long), 5),
         lat  = round(as.numeric(lat), 5))

# Create SpeciesType column and final selection.
df4 <- df3 %>%
  mutate(SpeciesType = ifelse(grepl("Cervus|Sus|Meles|Vulpes|Genetta|Herpestes", AnimalSpecies, ignore.case = TRUE), "Mammal", "Bird")) %>%
  select(PlantSp, Plant_ID, AnimalSpecies, DateTime, Behaviour, Coexistence, N_cam, EffortRev, EffortSpecies, EffortInd, duration, long, lat, SpeciesType)


sort(unique(df4$Coexistence))

df4 %>%
  group_by(Coexistence)%>%
  summarise(n =n())

```





