---
title: "Doñana_frugyvory_camptrap"
author: "PVA"
date: "6/7/2023"
output: html_document
---
The following script compiles some basic descriptors and graphics for the Doñana_frugivory camptrap datapaper. We present data summaries from phyto and zoocentric perspectives, basic trophic webs to show possible uses of the dataset.    

Libraries
```{r}
library(dplyr)
library(stringr)
library(tidyr)
library(bipartite)
library(ggplot2)
library(tidyverse)
library(lubridate)
library(av)
library(viridis)

#For activity
library(activity)
library(camtrapR)
library(overlap)
library(astroFns)
```
          

# PRELIMINARY ANALYSIS AND FIGURES
## 1. Load data
```{r }
sumhal_data <- read.csv("/Users/Pablo/Documents/GitHub/donana-frugivory-camtrap/Dataset_2023_07_19/DataS1.csv")
```

## 2. NETWORKS
```{r }
#------------------------------------------------------------------------------------------------
#Compare matrix for mammals vs birds
mammal <- sumhal_data %>%
     filter(SpeciesType == "Mammal")

bird <- sumhal_data %>%
     filter(SpeciesType == "Bird") 
    
mammal_mat <-  xtabs(~PlantSpecies + AnimalSpecies, mammal)
bird_mat <- xtabs(~PlantSpecies + AnimalSpecies, bird)

#BIRD WEB
# Define the species and color palette
species <- unique(bird$AnimalSpecies)
color_palette <- viridis(length(species))  # Adjust the colors as needed

# Create a named vector to map species to colors
species_color_mapping <- setNames(color_palette, species)

# Sort species names alphabetically
sorted_species <- sort(colnames(bird_mat))

# Rearrange the rows and columns of the bipartite matrix
sorted_bird_mat <- bird_mat[, sorted_species]
 
# Create the plot using Plotweb or your chosen bipartite network visualization tool
plotweb(sorted_bird_mat,
        method = "normal", 
  col.high = color_palette,
  col.interaction = color_palette,
  text.rot = 90,
  col.low = "grey90",
  bor.col.interaction = color_palette)

#MAMMAL WEB 
# Define the species and color palette
species <- unique(mammal$Sp1)
color_palette <- viridis(length(species))  # Adjust the colors as needed

# Create a named vector to map species to colors
species_color_mapping <- setNames(color_palette, species)

# Sort species names alphabetically
sorted_species <- sort(colnames(mammal_mat))

# Rearrange the rows and columns of the bipartite matrix
sorted_mammal_mat <- mammal_mat[, sorted_species]
 
# Create the plot using Plotweb or your chosen bipartite network visualization tool
plotweb(sorted_mammal_mat,
        method = "normal", 
  col.high = color_palette,
  col.interaction = color_palette,
  text.rot = 90,
  col.low = "grey90",
  bor.col.interaction = color_palette)

# ---------------------------- INDIVIDUAL WEBS ---------------------
#We use Rubus ulmifolius for the example change PlantSpecies for plotting other species   

#Individual level webs
rubus <- sumhal_data %>%
  filter(PlantSpecies == "Rubus ulmifolius") 

rubus_mat <- xtabs(~PlantID + AnimalSpecies, rubus)

# Sort species names alphabetically
sorted_df <- rubus[order(rubus$SpeciesType, rubus$AnimalSpecies), ]
sorted_species <- unique(sorted_df$AnimalSpecies)

color_palette <- viridis(length(sorted_species))  # Adjust the colors as needed

# Create a named vector to map species to colors
species_color_mapping <- setNames(color_palette, sorted_species)

# Rearrange the rows and columns of the bipartite matrix
sorted_rubus_mat <- rubus_mat[, sorted_species]
 
# Create the plot using Plotweb or your chosen bipartite network visualization tool
plotweb(sorted_rubus_mat,
  method = "normal",
  col.high = color_palette,
  col.interaction = color_palette,
  text.rot = 90,
  col.low = "grey90",
  bor.col.interaction = color_palette)
```

## 3. DOUBLE AXIS chart
   Sampling effort vs number of interactions charts
   Here we create a sampling effort bar chart for SPECIES and for individual plants
```{r }
#df with sampling effort by plant and number of interactions
df <- sumhal_data %>%
  select(PlantSpecies, EffortSpecies) %>%
  group_by(PlantSpecies)%>%
  summarise(eff = first(EffortSpecies),
            n= n())

#Plot sampling effort and number of interactions together
#Scale factor
scaleFactor <- max(df$eff) / max(df$n)

#Plot
ggplot(df, aes(x = fct_reorder(PlantSpecies, desc(n)),  width=.4)) +
  geom_col(aes(y=eff), fill="powderblue", position = position_nudge(x = -.4)) +
  geom_col(aes(y=n * scaleFactor), fill="indianred2") +
  scale_y_continuous(name="Sampling effort", sec.axis=sec_axis(~./scaleFactor, name="Number of interactions")) +
  xlab("Plant species") + 
  theme(
    axis.title.y.left=element_text(color="deepskyblue4"),
    axis.text.y.left=element_text(color="deepskyblue4"),
    axis.title.y.right=element_text(color="firebrick3"),
    axis.text.y.right=element_text(color="firebrick3"),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black"),
    axis.text.x = element_text(angle = 60, hjust = 1)) 

```

## 4. RECORDINGS by species 
Figure Animal Species recorded  x = number of records per species y = species names
```{r }
mammal <- sumhal_data %>%
     filter(SpeciesType == "Mammal") %>%
  group_by(AnimalSpecies) %>%
  summarise(n(),
            SpeciesType = first(SpeciesType)) %>%
  data.frame()%>%
  mutate(Sp1 = str_to_sentence(AnimalSpecies))%>%
  arrange(desc(n..)) 

bird <- sumhal_data %>%
     filter(SpeciesType == "Bird") %>%
  group_by(AnimalSpecies)%>%
  summarise(n(),
            SpeciesType = first(SpeciesType)) %>%
  data.frame()%>%
  mutate(Sp1 = str_to_sentence(AnimalSpecies))%>%
  #filter(n.. > 10)%>%
  arrange(desc(n..))

#bind mammals and birds and order each group by species Type 
df <- rbind (mammal, bird)
df$AnimalSpecies <- factor(df$AnimalSpecies, levels = df$AnimalSpecies[order(df$n..)])

ggplot(df, aes(x = n.., y = fct_reorder(AnimalSpecies, SpeciesType), fill = SpeciesType)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Number of Events", y = "Species", fill = "Type") +
  theme(axis.text.y = element_text(size = 5),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"))
  
```

## 5. ACTIVITY patterns
      Preliminary script and Denisty plots for activity patterns in Doñana frugivores. 
```{r }
# ----------------  1.Convert the data for later analysis 
  # Convert time into radians (Check dates for timestamp issues). 
radians <- gettime(sumhal_data$DateTime, format= "%Y-%m-%d %H:%M:%S", scale = "radian" )
date <- as.POSIXct(sumhal_data$DateTime, format = "%Y-%m-%d %H:%M:%S") #Date as.POSIXct
time <- date %>%
  str_sub (start =12L, end = 20)

  #solartime() transforms clock time to solar time anchored to sun rise and sunset times for a given location.
solartime <- solartime(date, lat= 37.0000000 , long= -6.3333300,tz= 2  ,"%y-%m-%d %H:%M:%S")
solar <- solartime$solar #Create new column with solar time
solar_input <- solartime$input

  #Dataset for analizing activity patterns 
act_data <- sumhal_data %>%
  cbind(radians, date, solar, solar_input, time) %>%
  select(AnimalSpecies, PlantSpecies, DateTime, date, Behaviour, solar, time) %>%
  filter(PlantSpecies != "Pistacia lentiscus" )

    #Construct df for two plant species
aspa <- act_data %>%subset(PlantSpecies == "Asparagus aphyllus")
rulm <- act_data %>%subset(PlantSpecies == "Rubus ulmifolius")

#-----------------   2. Analysis
# 2.1 Plot activity for one species (example)
activityDensity(recordTable = aspa, species = "Sylvia melanocephala", speciesCol = "AnimalSpecies", recordDateTimeCol = "date", recordDateTimeFormat = "%Y-%m-%d %H:%M:%S", plotR = TRUE)

# 2.2 Compare activity of two species (example)
activityOverlap (recordTable = rulm, speciesA    = "Sylvia melanocephala" , speciesB = "Sylvia communis", plotR = TRUE, linewidth = c(2.5, 2.5), 
                 linetype = c(1,1), linecol = c("#4682B4", "#D7C26F"), olapcol = "#FFFFE0",
                 add.rug     = TRUE, speciesCol = "AnimalSpecies", recordDateTimeCol = "date",  recordDateTimeFormat = "%Y-%m-%d %H:%M:%S", addLegend = FALSE)
```

## 6. RAREFACTION curves
```{r }
 # Here we plot the species accumulation curve using PAIRWISE INTERCTIONS instead of species and individual plants as sites. Therefore we we plot the Interaction accumulation curve (IAC) performed similarly as species diversity accumulation curve analysis considering each pairwise-interaction as a “species” and the different Plant individuals as sampling units (Jordano 2016). 

#Summarise number of foraging species in individual plants
df <- sumhal_data %>%
   mutate(pl = str_sub(PlantID, start = 1L, end = 4),
         pairwise_int = str_c(pl, AnimalSpecies, sep = "_"))%>%
  group_by(PlantID, pairwise_int) %>%
  summarise(n_interactions = n())
  
#Transpose the dataframe into an observation matrix where each row is the data collection in each of the plant individuals. Columns are frugivore species
obs <- df %>%
  pivot_wider(names_from= pairwise_int, values_from= n_interactions, 
                     values_fill= list(count= 0)) %>%
  replace(is.na(.), 0) 

sp2<-specaccum(obs[,-c(1:3)])

plot(sp2, ci.type="poly", col="blue", lwd=2, ci.lty=0, ci.col="lightblue",
      xlab = "Number of plant individuals", ylab = "Interaction richness")


#Obtain Species Richness estimators (Species richness/PlantID):
specpool(obs[,-c(1:3)],obs$PlantID)
 
```





